A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-02-19 src/tex/ms.tex
Manuscript updates

\begin{figure*}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
    \caption{Evolution of the MDF across the Galactic disk. Each panel presents the normalized stellar [Fe/H] distribution within a {2 kpc}-wide annulus, color-coded by the age bin. Rows (a) and (b) present the distributions from multi-zone GCE models, while row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}). The vertical dotted lines in row (c) mark the mode of the distribution in the $0-2\,{\rm kpc}$ age bin. Distributions are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex} in all panels.}
    \label{fig:mdf-evolution}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/mdf_evolution.pdf}
    \caption{Evolution of the MDF across the Galactic disk. Each panel presents the normalized stellar [Fe/H] distribution within a {2 kpc}-wide annulus, color-coded by the age bin. Rows (a) and (b) present the distributions from multi-zone GCE models, while row (c) presents the distributions from APOGEE DR17 with ages derived from [C/N] abundances (see Section \ref{sec:observational-sample}). The vertical blue dotted lines in row (c) mark the mode of the distribution in the $1-2\,{\rm kpc}$ age bin for reference. Also in row (c), the gray dashed line marks the cut at ${\rm [Fe/H]}>-0.4$ for upper red giant branch and red clump stars, and the gray solid line marks the cut at ${\rm [Fe/H]}<+0.45$ for all stars with [C/N]-based ages. Distributions in all panels are restricted to $0\leq|z|<0.5\,{\rm kpc}$ and boxcar-smoothed with a width of {0.1 dex}.}
    \label{fig:mdf-evolution}
\end{figure*}
